Clean and Process Raw Data

### 2020-03-09 data-raw/README.Rmd
Fix issue in 2015 Tiller ShB incidence AUDPS on line 714

TShB_perc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  arrange(PLOT)

TShB_perc_wide <-
  reshape2::dcast(TShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")

@@

LShB_perc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  arrange(PLOT)

LShB_perc_wide <-
  reshape2::dcast(LShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_LShB_PERCENT")

TShb_inc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
               .vars = vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  arrange(PLOT) %>%
  group_by(YEAR, REP, TRT, PLOT) %>%
  summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))

@@

TShB_perc_16 <-
  DS2016 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  arrange(PLOT)

TShB_perc_wide <-
  reshape2::dcast(TShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")

@@

LShB_perc_16 <-
  DS2016 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  arrange(PLOT)

LShB_perc_wide <-
  reshape2::dcast(LShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_LShB_PERCENT")

>>>>

TShB_perc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_percent = PERC_TIL_ShB)) %>%
  arrange(PLOT)

TShB_perc_wide <-
  reshape2::dcast(TShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_percent")

@@

LShB_perc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_LShB_percent = PERC_LEAF_ShB)) %>%
  arrange(PLOT)

LShB_perc_wide <-
  reshape2::dcast(LShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_LShB_percent")

TShB_inc_15 <-
  DS2015 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
               .vars = vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  arrange(PLOT) %>%
  group_by(YEAR, REP, TRT, PLOT) %>%
  summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))

TShB_inc_AUDPS <-  pull(TShB_inc_15, AUDPS)

@@

TShB_perc_16 <-
  DS2016 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_TShB_percent = PERC_TIL_ShB)) %>%
  arrange(PLOT)

TShB_perc_wide <-
  reshape2::dcast(TShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_TShB_percent")

@@

LShB_perc_16 <-
  DS2016 %>%
  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
                      .vars = vars(PLOT_LShB_percent = PERC_LEAF_ShB)) %>%
  arrange(PLOT)

LShB_perc_wide <-
  reshape2::dcast(LShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_LShB_percent")
